---
title: "p8105_hw1_sl5232"
author: "Shangsi Lin"
date: 2022-09-23
output: github_document
---

# Problem 1
## Load data and tidyverse

```{r chunk_setup}
library(tidyverse)
data("penguins", package = "palmerpenguins")
```

## Short description of the penguin dataset
The penguins dataset includes information about `r names(penguins)` of the individuals of interest.

The row size of the penguins dataset is `r nrow(penguins)` and the column size of the dataset is `r ncol(penguins)`.

The mean flipper length of the penguins dataset is `r mean(pull(penguins,flipper_length_mm), trim = 0, na.rm = TRUE)`

## Making and saving a scatterplot of flipper length(y) vs. bill length(x), different colors represent different species.
```{r chunk_flipper_vs_bill_scatterplot}
flipper_vs_bill_scatterplot_df =
  tibble(
    x = penguins$bill_length_mm,
    y = penguins$flipper_length_mm,
    species = penguins$species
  )

flipper_vs_bill_scatterplot = ggplot(flipper_vs_bill_scatterplot_df, aes(x,  y, color = species)) + geom_point()
print(flipper_vs_bill_scatterplot + labs(y = "flipper length(mm)", x = "bill length (mm)"))
ggsave("flipper_vs_bill_scatterplot.pdf")
```



```{r}

```


